---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Cailey Fay"
date: "3.17.26"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
library(robotstxt)
```

## Getting Started 
```{r}
paths_allowed("https://collections.ed.ac.uk/art)")
```

## Excercises 1-9: Creating the function and automating 
```{r}
source("scripts/01-scrape-page-one.R")
source("scripts/02-scrape-page-function.R")
source("scripts/03-scrape-page-many.R")
```

Now, load the dataset. **when I source above, it includes the dataframe that was created with all of the info, so I will be using that, but this code does work if I were so inclined to use it. 

```{#r load-data, message = FALSE, eval = TRUE}
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 10

Let's start working with the **title** column by separating the title and the date:  
The warning is just saying that pieces without the date in the format we are expecting are assigned NAs. 
```{r separate-title-date, error = TRUE}
auto <- auto %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  # Fill in the missing variable!
```

## Exercise 11  
There are 108 pieces with missing artists and 1574 with missing dates. 
```{r}
skim(auto)
```
## Exercise 12  
There was a painting with year = 2, which I filtered out so that the histogram was more interpretable. Otherwise, it looks like most of the paintings are from 1950 onward. 
```{r}
auto %>%
  filter(year > 2) %>%
ggplot(mapping = aes(x=year)) +
  geom_histogram(binwidth = 20)
```

## Exercise 13 
Death Mask by H. Dempshall was assigned year = 2. It was actually made in 1964, but in the title, there is a (2) before the (1964). Now it is fixed. 
```{r}
auto<- auto %>%
  mutate(year = case_when(
    year == 2 ~ 1964,
    TRUE ~ year
  ))
```

## Exercise 14 
There are 371 unknown artists. After that, the artist with the most pieces is Emma Gillies, with 174. I don't know them. 
```{r}
auto %>%
  count(artist) %>%
  arrange(desc(n))
```

## Exercise 15 
There are 11 pieces with child in the title. The website search says there are 43, but only 11 show up in my frame when I manually search. 
```{r}
child <- str_detect(auto$title, "Child")
table(child)

#this code shows up false for every piece
str_detect(auto$title, "child")
```


